prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-07-06 inst/MyArticle/paper.Rmd
fix

# read combined_protein.tsv 
protein <- prolfqua::tidy_MSFragger_combined_protein_deprec(protein)
# remove proteins identified by a single peptide
protein <- protein |> dplyr::filter(unique.stripped.peptides > 1)

>>>>

# read combined_protein.tsv 
protein <- prolfqua::tidy_FragPipe_combined_protein_deprec(protein)
# remove proteins identified by a single peptide
protein <- protein |> dplyr::filter(unique.stripped.peptides > 1)
